Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-19 snapshot_system/challenge.tex
revise intro/background/challenge

% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{itemize}
\item {\em Cluster-based backup storage.}
We use a distributed file system~\cite{GFS2004,Hadoop}  to cluster
the storage  and store the backup with multiple replicas in the clustered storage.
There can be a concern that storing many versions  of snapshots would
require	a large amount of storage.
The previous research shows the deduplication can compress the backup copies 
effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
ratio is $c$:1.  When the number of versions
saved in the backup storage is $l$  on the average, 
the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
When $l=9$ and $c=13$, storage usage is 40\%. 
That is acceptable given today's cheap cost for disk storage.
In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data
while each machine typically can provide over 10TB storage.
Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
extra space for the backup is not a practical concern.

@@

%\item {\em Requirement for backup throughput and low computing resource usage}.
Because of collocation of this snapshot service with other existing cloud services, 
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed can be huge. 
the computing resources allocated for a snapshot service is limited
because of its lower priority.  
The key usage of resource for backup is memory for storing and comparing the fingerprints. 
We will consider the approximation techniques with less memory consumption
studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
%and comparison.  This competes memory resource  with the existing VMs.
%Our design is to identify a low-cost and low-profile scheme for deduplication.
%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.

A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
the existing cloud, which is not preferred for cloud production system operation. 
Thus it is desirable that backup for all nodes
can be conducted in parallel and in a short period of time,
and any centralized or  cross-machine communication for
deduplication should not become a bottleneck.
For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
the system must finish saving daily snapshots of all VMs in a few hours. 
Often a cloud has a few hours of light workload each day (e.g. midnight),  
which creates an small window for automatic backup.
The backup service can generate hundreds of terabytes of data in such a time window
without optimization and thus the resource content is considered carefully as we design
a fault-resilient cluster-based solution. 
%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.

>>>>

% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{itemize}
\item {\em Collocating with cluster-based cloud services.}
We collocate the backup service with other cloud serices in a cluster
and  use a distributed file system~\cite{GFS2004,Hadoop}  to 
store the backup with multiple replicas. 
There can be a concern that storing many versions  of snapshots would
require	a large amount of storage.
The previous research shows the deduplication can compress the backup copies 
effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
ratio is $c$:1.  When the number of versions
saved in the backup storage is $l$  on the average, 
the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
When $l=9$ and $c=13$, storage usage is 40\%. 
That is acceptable given today's cheap cost for disk storage.
In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data
while each machine typically can provide over 10TB storage.
Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
extra space for the backup is not a practical concern.

@@

%\item {\em Requirement for backup throughput and low computing resource usage}.
Because of collocation of this snapshot service with other existing cloud services, 
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed can be huge. 
the computing resources allocated for a snapshot service is limited
because of its lower priority.  
The key usage of resource for backup is memory for storing and comparing the fingerprints. 
We will consider the approximation techniques with less memory consumption
studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
%and comparison.  This competes memory resource  with the existing VMs.
%Our design is to identify a low-cost and low-profile scheme for deduplication.
%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
the existing cloud, which is not preferred for cloud production system operation. 
Thus it is desirable that backup for all nodes
can be conducted in parallel and in a short period of time,
and any centralized or  cross-machine communication for
deduplication should not become a bottleneck.
For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
the system must finish saving daily snapshots of all VMs in a few hours. 
Often a cloud has a few hours of light workload each day (e.g. midnight),  
which creates an small window for automatic backup.
The backup service can generate hundreds of terabytes of data in such a time window
without optimization and thus the resource content is considered carefully as we design
a fault-resilient cluster-based solution. 
%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.

### 2013-06-19 snapshot_system/snapshot.tex
modify analysis
revise intro/background/challenge

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
The tradition approach compares all fingerprints and 
reserve one copy for all of its deduplicates.
We call this as  the VM-oblivious (VO) approach.
In comparison, we analyze the design of
a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
and conducts \textit{Inner-VM} and \textit{cross-VM} detection.

@@

\item \textbf{Chunk-level fine-grain nearby duplicate detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\subsection{Popular Chunk Management}
%VM-oriented Fault Isolation}
%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
%in the cluster.  
%The inner-VM deduplication does not depend on any global service and the comparison
%for each VM is localized within the parent and the current snapshot.
%Lack of data dependence between VMs brings 
With cross-VM deduplication, shared data blocks
create an artifical dependence  among VMs and failure of one shared block
affects many VMs. Thus we only maintain the index for a small set of popular chunks.
The mnagement for popular data chunks contains two aspects.
\begin{itemize}
\item Compute and select top-$k$ most popular chunks.
The popularity of a chunk is the number  of data blocks from different VMs
that are duplicates of this block after the inner VM deduplication.
This number can be computed perioidically in a weekly basis.
Once the popularity of all data blocks is collected, the system only maintains the top $k$
most popular blocks.
\item  Top $k$ number is chosen to be small while 
our analysis belows will show that the algorithm can still deliver competitive deduplication effiency.
Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
We will provide an alaysis in the next subsection.
\end{itemize}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
\hline
$b$ &  the total amount of data blocks\\ 
\hline
$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
\hline
$C_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$s$ &  the percentage of duplicates detected in inner VM deduplication\\
\hline
$s$ &  the percentage of duplicates detected in inner VM deduplication\\
\hline
$p$ & the number of nodes in the cluster\\
\hline
$D$ & the amount of unique data on each node\\
\hline
$B$ & the average block size\\
\hline
$m$ & memory size on each node used by VC\\ 
\hline
$F$ & the size of an polular data index entry\\
\hline
\end{tabular}
\caption{Modeling  symbols.}
\label{tab:symbol}
\end{table}

@@

Deduplication efficiency of VC using top $k$ popular blocks
is the percentage of duplicates that can be detected:  
\begin{equation}
\begin{split}
e_k &= 
\frac{ b(1-s) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
{b(1-s)  + sb - b_u }\\
&= 
\frac{ (1-s) + s (\frac{k}{b_u})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\end{split}
\end{equation}

@@

The overall deduplication effiency is
\[
\frac{ (1-s) + s (\frac{m*B}{D*F})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\]
where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining blocks detected as duplicates
after inner VM deduplication. 
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}

>>>>

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
The tradition approach compares all fingerprints and 
reserve one copy for all of its deduplicates.
We call this as  the VM-oblivious (VO) approach.
In comparison, we analyze the design of
a VM-centric approach (VC) which differenates duplicates within a VM and cross VMs,
and conducts \textit{Inner-VM} and \textit{cross-VM} detection seperately.

@@

\item \textbf{Chunk-level fine-grain inner-VM detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}.
Thus the second-level inner-VM deduplication is to assess in this
level, but only for those dirty  segments. 
We load the fingerprints of block chunks of the corresponding segment from the
parent for a comparisons and compare near-by fingerprint matching within this segement.
The amount of memory for maintaining those fingerprints  is small.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

When a block is not detected as a duplicate to any existing block, this block will be written
to the file system. Since the backend file system typically uses a large block size such as 64MB, each VM will 
accumnulate small local blocks. We manage  this accmulation process using an apendstore  scheme
and discuss this in details in Section~\ref{sect:arch}.

 \subsection{Popular Chunk Management}
%VM-oriented Fault Isolation}
%Our objective for fault isolation is to minimize the number of VMs affected when there are failures
%in the cluster.  
%The inner-VM deduplication does not depend on any global service and the comparison
%for each VM is localized within the parent and the current snapshot.
%Lack of data dependence between VMs brings 
With cross-VM deduplication, shared data blocks
create an artifical dependence  among VMs and failure of one shared block
affects many VMs. Thus we only maintain the index for a small set of popular chunks.
The mnagement for popular data chunks contains two aspects.
\begin{itemize}
\item Compute and select top-$k$ most popular chunks.
The popularity of a chunk is the number  of data blocks from different VMs
that are duplicates of this block after the inner VM deduplication.
This number can be computed perioidically in a weekly basis.
Once the popularity of all data blocks is collected, the system only maintains the top $k$
most popular blocks.  For cross-VM comparison,
we only store  top $k$ items and $k$ is  chosen to be small while 
our analysis belows will show that the algorithm can still deliver competitive deduplication effiency.
\item  Since $k$ is small and these top $k$ blocks are shared among multiple VMs, 
we can afford to provide extra replicas for these popular blocks to enhanace the fault resilence.
We will provide an alaysis in the next subsection.
\end{itemize}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
\hline
$b$ &  the total amount of data blocks\\ 
\hline
$b_u$ &  the total amount of unique fingerprints after inner VM  deduplication\\
\hline
$C_i$ &  the frequency for the $i$th most popular fingerprint\\
\hline
$\delta$ &  the percentage of duplicates detected in inner VM deduplication\\
\hline
$p$ & the number of nodes in the cluster\\
\hline
$D$ & the amount of unique data on each node\\
\hline
$B$ & the average block size. Our setting is  4K.\\
\hline
$s$ & the average size of data containers stored in the distributed file system . Our setting is  64MB.\\
\hline
$m$ & memory size on each node used by VC\\ 
\hline
$F$ & the size of an polular data index entry\\
\hline
\end{tabular}
\caption{Modeling  symbols.}
\label{tab:symbol}
\end{table}

@@

Deduplication efficiency of VC using top $k$ popular blocks
is the percentage of duplicates that can be detected:  
\begin{equation}
\begin{split}
e_k &= 
\frac{ b(1-\delta) + C_1\frac{  k^{1-\alpha}} {1-\alpha}} 
{b(1-\delta)  + sb - b_u }\\
&= 
\frac{ (1-\delta) + s (\frac{k}{b_u})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\end{split}
\end{equation}

@@

The overall deduplication effiency is
\[
\frac{ (1-\delta) + \delta (\frac{m*B}{D*F})^{1-\alpha}}
{ 1- \frac{b_u}{b} }.
\]
where $(\frac{m*B}{D*F})^{1-\alpha}$ represents the percentage of the remaining blocks detected as duplicates
after inner VM deduplication. 
%Then the deduplication efficiency of CDS approach using top k most popular fingerprints is:
%\begin{equation}
%  e_k = (\frac{m*B}{F*D})^{1-\alpha}
%\end{equation}
